### 2019-08-07 defesa/tex/appendix/3pnts_ellipse_1.tex
wip

\begin{equation}
\varphi(p)=\left[\begin{array}{c}
\frac{b}{a}(\dfrac{t^2-1}{t^2+1}p_x + \dfrac{2t}{t^2+1}p_y)\\
\dfrac{t^2-1}{t^2+1}p_y - \dfrac{2t}{t^2+1}p_x\\
\end{array}\right],
\end{equation}

Thus $\varphi(p_1), \varphi(p_2), \varphi(p_2)$ can be written as quotients of polynomials on of degree $2$.

@@

Replacing the points by $\hat{p_1}, \hat{p_2}, \hat{p_3}$, we get:

\begin{eqnarray*}
\left|
\begin{array}{cccc}
x^2+y^2&x&y&1\\
0&0&0&1\\
\hat{p}_{2x}^2+\hat{p}_{2y}^2&\hat{p}_{2x}&\hat{p}_{2y}&1\\
\hat{p}_{3x}^2+\hat{p}_{3y}^2&\hat{p}_{3x}&\hat{p}_{3y}&1\\
\end{array}
\right| = 0\\
(x^2+y^2)\left|
\begin{array}{cc}
\hat{p}_{2x}& \hat{p}_{2y}\\
\hat{p}_{3x}& \hat{p}_{3y}
\end{array}\right|
+
x\left|
\begin{array}{cc}
	\hat{p}_{2x}^2+\hat{p}_{2y}^2& \hat{p}_{2y}\\
	\hat{p}_{3x}^2+\hat{p}_{3y}^2& \hat{p}_{3y}
\end{array}\right|
y\left|
\begin{array}{cc}
	\hat{p}_{2x}& \hat{p}_{2x}^2+\hat{p}_{2y}^2\\
	\hat{p}_{3x}& \hat{p}_{3x}^2+\hat{p}_{3y}^2
\end{array}\right|=0.
\end{eqnarray*}

We need to determine the radius of the circle and find the value of $t$, so the radius is equal to $b$. Rearranging the terms we obtain the expression:

\begin{equation}\label{eq:le3}
\dfrac{\left|
	\begin{array}{cc}
	\hat{p}_{2x}& \hat{p}_{2x}^2+\hat{p}_{2y}^2\\
	\hat{p}_{3x}& \hat{p}_{3x}^2+\hat{p}_{3y}^2
	\end{array}\right|^2
+\left|
\begin{array}{cc}
\hat{p}_{2x}^2+\hat{p}_{2y}^2& \hat{p}_{2y}\\
\hat{p}_{3x}^2+\hat{p}_{3y}^2& \hat{p}_{3y}
\end{array}\right|^2
}{4\left|
\begin{array}{cc}
\hat{p}_{2x}& \hat{p}_{2y}\\
\hat{p}_{3x}& \hat{p}_{3y}
\end{array}\right|^2} = b^2,
\end{equation}

After replacing \autoref{eq:trpnts} on \autoref{eq:le3}, we obtain a polynomial of degree $12$, which gives an upper-bound of $12$ to the number of solutions.

Nevertheless, because ellipses are symmetrical over their major-axis, we only need to consider rotations on the range $[0, \pi]$ as $\theta$ and $\theta+\pi$ represent the exact same solution geometrically. This ends up halving the upper-bound to $6$.

>>>>

\begin{equation}
\varphi(p)=\left[\begin{array}{cc}
\dfrac{b}{a}\dfrac{t^2-1}{t^2+1}& \dfrac{b}{a}\dfrac{2t}{t^2+1}\\
\dfrac{t^2-1}{t^2+1}& -\dfrac{2t}{t^2+1}\\
\end{array}\right]p.
\end{equation}

Thus $\varphi(p_1), \varphi(p_2), \varphi(p_2)$ can be written as quotients of univariate polynomials of degree $2$.

@@

As for this problem $(x_1, y_1)=(0,0)$, we can rewrite \autoref{3pnt_circle} as:

\begin{equation}
\left|
\begin{array}{ccc}
x^2+y^2&x&y\\
x_2^2+y_2^2&x_2&y_2\\
x_3^2+y_3^2&x_3&y_3
\end{array}
\right| = 0.
\end{equation}

Expanding the determinant we get:

\begin{equation*}
(x^2+y^2)\left|
\begin{array}{cc}
x_2&y_2\\
x_3&y_3
\end{array}\right|
+
x\left|
\begin{array}{cc}
x_2^2+y_2^2&y_2\\
x_3^2+y_3^2&y_3
\end{array}\right|
+
y\left|
\begin{array}{cc}
x_2&x_2^2+y_2^2\\
x_3&x_3^2+y_3^2
\end{array}\right|=0.
\end{equation*}

After completing the square we obtain \autoref{eq:le3} which is an expression for the radius of the circle, which has to be equal $b$.

\begin{equation}\label{eq:le3}
\dfrac{\left|
	\begin{array}{cc}
	x_2^2+y_2^2&y_2\\
	x_3^2+y_3^2&y_3
	\end{array}\right|^2
+\left|
\begin{array}{cc}
x_2&x_2^2+y_2^2\\
x_3&x_3^2+y_3^2
\end{array}\right|^2
}{4\left|
\begin{array}{cc}
x_2&y_2\\
x_3&y_3
\end{array}\right|^2} = b^2.
\end{equation}

We want to show that \autoref{eq:le3}, after replacing $(x_2, y_2)$ and $(x_3, y_3)$ with $\varphi(p_2)$ and $\varphi(p_3)$, is a polynomial on $t$ of degree $12$. As the denominator of $\varphi(p)_x$ and $\varphi(p)_y$ are the same, we can ignore it as it cancels out when it is equal to $0$. Let us analyze one of the determinants from the numerator of \autoref{eq:le3} which is the term with the highest degree.

\begin{equation}\label{eq:num1}
\left|
	\begin{array}{cc}
	||\varphi(p_2)||^2&\varphi(p_2)_y\\
	||\varphi(p_3)||^2&\varphi(p_3)_y
	\end{array}\right|^2=(||\varphi(p_2)||^2\varphi(p_3)_y-||\varphi(p_3)||^2\varphi(p_2)_y)^2.
\end{equation}

As $||\varphi(p_2)||^2$ has degree $4$ and $\varphi(p_3)_y$ has degree $2$ (ignoring the denominator), after multiplying and squaring we arrive at the conclusion that the polynomial has degree $12$.

\section{Final Remarks}

Expressing the actual polynomial would take too much space, and actually finding every one of its roots is a very expensive task computationally, so just determining its degree was enough for what we wanted to show.

Also, ellipses are symmetrical with respect to their major-axis which means that an ellipse is identical to itself rotate by $\pi$. Because of that, any solution found has a symmetrical one, which is obtained by adding $\pi$ to it. This halves the upper-bound for the number of solutions to $6$.
